Donor Responses to Civil Society Repression

### 2024-11-01 README.qmd
oof fix project name heading

## `r emoji_glue(":candy::bat:")`: Note on "butterscotch bat
Because project titles change all the time with revisions, rewriting, and peer review, we used [{codename}](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won’t change.

>>>>

## `r emoji_glue(":candy::bat:")`: Note on "butterscotch bat" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [{codename}](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won’t change.
